---
title: "Lab 8"
subtitle: "Cheese Gromit!"
editor: source
---

> **Goal:** Scrape information from <https://www.cheese.com> to obtain a dataset
> of characteristics about different cheeses, and gain deeper insight into your
> coding process. 🪤

```{r}

library(rvest)
```


## **Part 1:** Locate and examine the `robots.txt` file for this website. Summarize
what you learn from it.

<https://www.cheese.com/robots.txt>
User-agent: *
Sitemap: https://www.cheese.com/sitemap.xml

User-agent: *: anyone is allowed to scrape
No Crawl-delay: no wait time is required between each page scraped
No Visit-time entry: no restrictions on time that scraping is allowed
No Request-rate entry: no restrictions on simultaneous requests
No mention of Disallow sections

## **Part 2:** Learn about the `html_attr()` function from `rvest`. Describe how
this function works with a small example.

It gets the an attribute of a single html element. You can pull various details of an element, such as the reference link, the class, the name, the css styling etc. Below I have initialized a basic html. We  stated that the reference link for the first element is a.com and that the class is 'vital'. For the second we do the same but with href being alisa.com and the class being '541'. For the last we can see when the attribute is outside of the <a></a> it is not recognized as an attribute. Thus the class, "active" is not pulled, but the href, harshini.com is pulled.

```{r}

# below we initialize a basic html
html <- minimal_html('<ul>
  <li><a href="https://cheese.com" class="vital">a</a></li>
  <li><a href="https://alisa.com" class="541" >b</a></li>
  <li>class="active"<a href="https://harshini.com">b</a></li>
  </ul>')

# here we run the function to pull the attributes we wrote
html %>% html_elements("a") %>% html_attrs()


```


## **Part 3:** (Do this alongside Part 4 below.) I 
used [ChatGPT](https://chat.openai.com/chat) to start the process of scraping
cheese information with the following prompt:

> Write R code using the rvest package that allows me to scrape cheese
> information from cheese.com.

Fully document your process of checking this code. Record any observations you
make about where ChatGPT is useful / not useful.

```{r}
#| eval: false
#| label: small-example-of-getting-cheese-info

# Load required libraries: already have a libraries code chunk, and reloading the libraries every time, feels inefficient, but not incredibly so. 
library(rvest) 
library(dplyr)


# Define the URL: this seems to be correct and defining this individually makes it easier should we need to change the url or use it somewhere else
url <- "https://www.cheese.com/alphabetical"

# Read the HTML content from the webpage: 
webpage <- read_html(url)

# Extract the cheese names and URLs
cheese_data <- webpage %>%
  html_nodes(".cheese-item") %>%
  # cheese-item is non-existent, this should be h3 a, as when we ran that we had legitimate output
  html_nodes("a") %>%
  html_attr("href") %>%
  paste0("https://cheese.com", .)
  #the outcome of this is "https://cheese.com" which is not what we would want: so the paste0 function is useless
  # the general structure is useful though, and when you separate the flow and edit it to remove.cheese-item it seems to work


cheese_names <- webpage %>%
  html_nodes(".cheese-item h3") %>%
  # again .cheese-item is non-existent so we would want to remove that, but then it runs fine
  html_text()


# this works well, when the above is fixed
# Create a data frame to store the results
cheese_df <- data.frame(Name = cheese_names,
                        URL = cheese_data,
                        stringsAsFactors = FALSE)


# Print the data frame
print(cheese_df)
```



**Part 4:** Obtain the following information for **all** cheeses in the
database:

-   cheese name
-   URL for the cheese's webpage (e.g., <https://www.cheese.com/gouda/>)
-   whether or not the cheese has a picture (e.g., 
[gouda](https://www.cheese.com/gouda/) has a picture, but 
[bianco](https://www.cheese.com/bianco/) does not).

To be kind to the website owners, please add a 1 second pause between page
queries. (Note that you can view 100 cheeses at a time.)

**Part 5:** When you go to a particular cheese's page (like 
[gouda](https://www.cheese.com/gouda/)), you'll see more detailed information
about the cheese. For [**just 10**]{.underline} of the cheeses in the database,
obtain the following detailed information:

-   milk information
-   country of origin
-   family
-   type
-   flavour

(Just 10 to avoid overtaxing the website! Continue adding a 1 second pause
between page queries.)

**Part 6:** Evaluate the code that you wrote in terms of **efficiency**. To
what extent do your function(s) adhere to the **principles for writing good functions**?
To what extent are your **functions efficient**? To what extent is your 
**iteration of these functions efficient**? 